DATA 621 Homework #2

### 2019-10-07 hw2/HW2.Rmd
Updated HW2.Rmd

>>>>

## pROC Output

```{r}
par(pty = "s")
roc(df[[actual]], df[[predicted]], plot = TRUE, legacy.axes = TRUE, print.auc = TRUE)
par(pty = "m")
```

## Our ROC Curve

```{r}
our_roc <- roc_curve(df, actual, probability)

our_roc$plot
```

### F1 Score Will Always be Between 0 and 1
Before we move on, let’s consider a question that was asked: What are the bounds on the F1 score? Show that the F1 score will always be between 0 and 1. (Hint: If 0<a<1 and 0<b<1 then ab<a).

**Proving the range of the F1 Score must be between 0 and 1**

**Let's expand the F1 equation using the definitions of precision and sensitivity.**

$$\textrm{F1 Score}= \frac{2 \times\mathrm{Precision}\times\mathrm{Sensitivity}}{\mathrm{Precision}+\mathrm{Sensitivity}}$$ 
**The numerator is equal to**
$$=\frac{2 \times TP \times TP}{(TP + FP)(TP+FN)}$$ 
**The denominator is equal to**
$$= \frac{1}{\frac{TP}{TP+FP}+\frac{TP}{TP+FN}}$$  
**Combine the Numerator and the denominator:**
$$F1=\frac{2 \times TP \times TP}{(TP + FP)(TP+FN)} \times \frac{1}{\frac{TP}{TP+FP}+\frac{TP}{TP+FN}}$$  
**Multiply the denominator by (TP + FP)(TP + FN):**

$$denominator = \frac{(TP+FP)(TP+FN)}{TP(TP+FN)+TP(TP+FP)}$$  
$$F1=\frac{2(TP)^2}{(TP+FP)(TP+FN)}\times \frac{(TP+FP)(TP+FN)}{TP(TP+FN)+TP(TP+FP)}$$  
**Cancel the denominator of the first term with the numerator of the second term:**

$$F1 =\frac{2(TP)^2}{TP(TP+FN)+TP(TP+FP)}$$
**Simplify the Denominator:**
$$F1 =\frac{2(TP)^2}{TP^2+FNTP+TP^2+TPFP}$$  
$$F1 =\frac{2(TP)^2}{TP(TP+FN+TP+FP)}$$  
$$F1 =\frac{2(TP)^2}{TP(TP+FN+TP+FP)}$$  
$$F1 =\frac{2(TP)^2}{TP(2TP +FN +FP)}$$ 
**Cancel the TP terms and get final answer**
$$F1=\frac{2TP}{2TP+FN+FP}$$
<br>  
In the equation above, $TP,FN,FP \in \mathbb{N}$ where $\mathbb{N} = \{0,1,2,3...\}$

$2TP \le2TP+FN+FP$ this equation shows that the numerator is at most equal to the denominator (i.e $F1\le1$).

There would be a Maximum value of $1$ when $FN=FP=0$ and $TP > 0$

The fraction $=\frac{2TP}{2TP+FN+FP}$ has a minimum value of zero when the numerator is minimized (i.e. $TP=0$).

We have shown that $0\le F1\le1$
<br>
